---
title: "MATH 216 Homework 2 Shiny App"
author: "Alden Cowap"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(dplyr)
library(babynames)
library(ggplot2movies)
```


## Inputs and Outputs

You can embed Shiny inputs and outputs in your document. Outputs are automatically updated whenever inputs change.  This demonstrates how a standard R plot can be made interactive by wrapping it in the Shiny `renderPlot` function. The `selectInput` and `sliderInput` functions create the input widgets used to drive the plot.

```{r eruptions, echo=FALSE}
movie_data <- movies %>% mutate(Genre = ifelse(Comedy == 1, "Comedy", "Other"))

inputPanel(
  
  # Input comedy
  radioButtons("Genre", "Genre", c("Comedy" = "Comedy", "Other" = "Other"))

)

renderPlot({

  
  # Generate Plots
  movies2 <- movie_data %>%
    filter(!is.na(budget)) %>% 
    filter(Genre == input$Genre) 
  

    
  
  ggplot(data=movies2, aes(x=budget, y=rating)) + 
    geom_point() + scale_x_log10() + geom_smooth(se = FALSE) +
    labs(x = "Log of Budget", y = "Rating", title = "Budget vs. Rating")

 
  
})

renderPlot({
    
  movies3 <- movie_data %>%
    filter(!is.na(budget)) %>% 
    filter(Genre == input$Genre) %>% 
    group_by(budget) %>% 
    summarise(av_rating = mean(rating))
  
  ggplot(data=movies3, aes(budget, y= av_rating)) + geom_point() + 
    scale_x_log10() + geom_smooth(se=FALSE) +
    labs(x = "Log of Budget", y = "Average Rating", title = "Budget vs. Average Rating")
  
})
```

For both Comedy movies and other genres, budget does not seem to have a causal effect on rating or average rating. 
